---
title: "RDBMtoNoSQL"
author: "Rajwant Mishra"
date: "April 18, 2019"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---

# Package 

```

library(tidyverse)
library(RMySQL)
library(DBI)
library(gridExtra)
library(mongolite)

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(RMySQL)
library(DBI)
library(gridExtra)
library(mongolite)

USER = "msds_user"
PASS = "msds"
HOST = "cluster0-bqyhe.gcp.mongodb.net"
URI = sprintf("mongodb+srv://%s:%s@%s/", USER, PASS, HOST)






NOSQL_CON = mongo(collection = "movie", db = "MSDS_Review", url = URI) # create connection, database and collection


NOSQL_ALL = mongo( url = "mongodb+srv://msds_user:msds@cluster0-bqyhe.gcp.mongodb.net/") # create connection, database and collection


```

# Read/Write {.tabset .tabset-fade .tabset-pills}

## Read Data from MySQL 


```{r}

# install.packages("RMySQL")

 con2 <- dbConnect(RMySQL::MySQL(), dbname = "flights", host="localhost", user="root",password= "")
 

dbListTables(con2)

 # Database Operation 
con2 <- dbConnect(RMySQL::MySQL(), dbname = "flights", host="localhost", user="root",password= "")
query <- "SELECT * FROM movies_review"

tab1 <- dbSendQuery(con2,query)
suppressWarnings(rm(movies_review ))
movies_review <- dbFetch(tab1)

query <- "SELECT * FROM movies_master"

tab1 <- dbSendQuery(con2,query)
movies_master <- dbFetch(tab1)

DT::datatable(movies_master)
DT::datatable(movies_review)


 
```


## Move to Mongo {.tabset .tabset-fade .tabset}

We are creating two colelction for this data, one for Movie and Movei_Review

### Upload

```{r}


# Using plain-text
URI = sprintf("mongodb+srv://%s:%s@%s/", USER, PASS, HOST)
OpenCon<- mongo(url = URI)

#Deault is Test colelction 
OpenCon

# Lets create new colection MOvie

CON_movie <- mongo("movie", db = "MSDS_Review",url=URI)


#Check what is in collection Movie
# empty the colelction
CON_movie$drop()         #Refresh the collection
CON_movie$count()        # COunt collection
CON_movie$insert(movies_master)
CON_movie$count()        # COunt collection

CON_movie$disconnect()
CON_movie$count()
# Lets create new colection MOvieR for Movie Reviews

CON_movieR <- mongo("movie_review", db = "MSDS_Review",url=URI)
CON_movieR$drop()      #Refresh the collection
CON_movieR$count()     # COunt collection
CON_movieR$insert(movies_review)
CON_movieR$count()     # COunt collection

```

### Query on Data 

 + count 
 + Find 
 + Create Index

```{r}

#View connection
CON_movie
CON_movieR

#Validation if data was moved successfuly to Mongo DB
ifelse(CON_movie$count()==nrow(movies_master),"movies_master All Data in Mongo","Something is not in Mongo")
ifelse(CON_movieR$count()==nrow(movies_review),"movies_review All Data in Mongo","Something is not in Mongo")

# Quick Way
CON_movieR$count()==nrow(movies_master)

#The empty query {} means: select all data. 
# Get all records
CON_movieR$count('{}')

## Read all the data back into R
CON_movieR$find()
CON_movieR$find('{}')



## To query all rows where User_Name == "TheTopDawg" AND Rating > 5 



CON_movieR$find('{"User_Name" : "TheTopDawg" ,"Rating":{"$gt":5}}')

#Read rating for Movie_ID = 1 and rating less than 5

subsetRevie  <- CON_movieR$find('{"Movie_ID" : 1 ,"Rating":{"$lt":5}}')

subsetRevie

#Using In , find all the movie rating for 1 and 2 where rating is less than 5  
subsetRevie12  <- CON_movieR$find('{"Movie_ID" :{"$in":[1,2]} ,"Rating":{"$lt":5}}')

subsetRevie12


# using Qury and Fields 
MR_Query_Fields <- CON_movieR$find(
  query = '{"Movie_ID" : 1 , "Rating" : {"$gt":5 }}', 
  fields = '{"ID" : true, "Rating" : true,"User_Name" : true,"Movie_ID":true}',
  limit = 5
)
print(MR_Query_Fields)

#sort by rating IN dESCENDING ORDER for Movie_ID = 1

CON_movieR$find('{"Movie_ID" : 1}' , sort = '{"Rating": -1}')   


# Check time , since by default Mongo has _id is the only index, and other field would be costly to the db 

system.time(CON_movieR$find('{"Movie_ID" : 1}' , sort = '{"Rating": -1}') )
system.time(CON_movieR$find('{"Movie_ID" : 1}' , sort = '{"_id": -1}') )

#lets add Movie_ID as Index 

CON_movieR$index(add = '{"Movie_ID" : 1}')
# Lets see how many index we have
CON_movieR$index()

# Check sysetm time taken for excecution now
system.time(CON_movieR$find('{"Movie_ID" : 1}' , sort = '{"Rating": -1}') )

```

### iterate

```{r}
# Lets use iterate to read data 
DT::datatable(CON_movieR$find())
Review_Iter <- CON_movieR$iterate('{"Movie_ID" : 1}', sort = '{"Rating": -1}', limit = 7)

# read records from  the iterator
while(!is.null(x <- Review_Iter$one())){
  cat(sprintf("Found Movie ID %s for USER : %s\n", x$Movie_ID, x$User_Name))
}

```

### Remove 

```{r}
# Lets say I want to remove all the rating of 4 for Movie 1
# 1 list those record
CON_movieR$find('{"Movie_ID" : 1,"Rating":{"$eq":4}}') 

# 2 : Remvoe 
CON_movieR$remove('{"Movie_ID" : 1,"Rating":{"$eq":4}}')

# 3 : Valdiate 
CON_movieR$find('{"Movie_ID" : 1,"Rating":{"$eq":4}}') 
CON_movieR$find('{"Movie_ID" : 1,"Rating":{"$ne":4}}') # not equal to 4

CON_movieR$count() # Count got reduced .

#Let update rating from 8 to 9

CON_movieR$find('{"Movie_ID" : 1,"User_Name":"krice23"}') 
CON_movieR$update('{"Movie_ID" : 1,"User_Name":"krice23"}','{"$set":{"Rating":9}}')
CON_movieR$find('{"Movie_ID" : 1,"User_Name":"krice23"}') 
# we should using multiple = TRUE if we want to udpate more that one record.


CON_movieR$find('{"User_Name":"TheTopDawg"}') 
CON_movieR$update('{"User_Name":"TheTopDawg"}','{"$set":{"Rating":9}}')
CON_movieR$find('{"User_Name":"TheTopDawg"}') 
# multiple = TRUE if we want to udpate more that one record.
CON_movieR$update('{"User_Name":"TheTopDawg"}','{"$set":{"Rating":7}}',multiple = TRUE)
CON_movieR$find('{"User_Name":"TheTopDawg"}') 

```

### Export and other function

Mongo stores data in BSON , we can get BSON output by passing BSON = true
```{r}
CON_movie$export()

CON_movie$export(file("mr.bson"),bson = TRUE)


OpenCon$run('{"listCollections":1}')

CON_admin <- admin <- mongo(db = "admin",url = URI)
CON_admin$run('{"listDatabases":1}')

```

### Distinct

```{r}

NOSQL_CON = mongo(collection = "movie", db = "MSDS_Review", url = URI) # create connection, database and collection
NOSQL_CON$index()
NOSQL_CON$count()
NOSQL_CON$distinct("Movie_Name")
DT::datatable(NOSQL_CON$find())
NOSQL_CON$iterate()$one()

# Find Movie with name "Incredibles 2"
# USe count to get the count of matching record . 
# use find to get the data

NOSQL_CON$count('{"Movie_Name" : "Incredibles 2"  }')
NOSQL_CON$count('{"Movie_Name" : "Incredibles2"  }') # Note space missing between name `Incredibles 2`.
NOSQL_CON$find('{"Movie_Name" : "Incredibles 2"  }')
MOview_Rating <- NOSQL_CON$find('{"ID" : 1}')
print(MOview_Rating)

```


# Compare Nosql and MYSQL

<table class="table table-bordered table-striped">
<tbody><tr><th>SQL Database</th><th>NoSQL Database (MongoDB)</th></tr>
<tr><td>Relational database</td><td>Non-relational database</td></tr>
<tr><td>Supports SQL query language</td><td>Supports JSON query language</td></tr>
<tr><td>Table based</td><td>Collection based and key-value pair</td></tr>
<tr><td>Row based</td><td>Document based</td></tr>
<tr><td>Column based</td><td>Field based</td></tr>
<tr><td>Support foreign key</td><td>No support for foreign key</td></tr>
<tr><td>Support for triggers</td><td>No Support for triggers</td></tr>
<tr><td>Contains schema which is predefined</td><td>Contains dynamic schema</td></tr>
<tr><td>Not fit for hierarchical data storage</td><td>Best fit for hierarchical data storage</td></tr>
<tr><td>Vertically scalable - increasing RAM</td><td>Horizontally scalable - add more servers</td></tr>
<tr><td>Emphasizes on ACID properties (Atomicity, Consistency, Isolation and Durability)</td><td>Emphasizes on CAP theorem (Consistency, Availability and Partition tolerance)</td></tr>
</tbody></table>

MongoDB is an open source document-oriented NoSQL database which stores data in the form of JSON-like objects. Hence a collection in MongoDB is equivalent to Table in relational database And a document in a collection in MongoDB is equivalent to a row in relational database table.

If we were using a relational database, we could perform a join on users and stores, and get all our objects in a single query. But MongoDB does not support joins and so, at times, requires bit of denormalization


NoSQL and relational databses differ in the manner they represent data. While a row stores data in columns, document stores in JSON like structure.

MongoDB documents support dynamic schema, i.e. documents in same collection can have different schema , one can have 5 fileds , while other can have more or less than five. This allows complex hierarchical /tree structured schemas is be efficiently stored in MongoDB.

Relationships in relational databse can be achieved through primary key /foreign key constraints ; No such mapping is present in MongoDB other than linking / emnbedding of documents .



# Ref
 + https://jeroen.github.io/mongolite/manipulate-data.html
 + https://cran.r-project.org/web/packages/mongolite/mongolite.pdf