---
title: "W7 607 Final"
author: "Rajwant Mishra"
date: "March 17, 2019"
output:
  html_document:
    toc: true
    theme: united
    df_print: paged
    highlight: tango

    
   
---

<style>

.section .level2 .tabset .nav-pills>li.active>a {
    color: #fff;
   background-color: #cc7c2d;
}	

.section .level2 .tabset .nav-pills>li.active>a, .nav-pills>li.active>a:focus, .nav-pills>li.active>a:hover {
    color: #fff;
   background-color: #cc7c2d;
}	

.section .level2 .nav-pills>li>a {
    border-radius: 50px;
}
</style>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Parsing of HTML/XML files  
library(rvest)    
# String manipulation
library(stringr)   
# Verbose regular expressions
#install.packages("rebus")
library(rebus)     
# Eases DateTime manipulation
library(lubridate)
library(DT)
#----------Woks with File 
library(mongolite)
library(gridExtra)
library(tidyverse)
library(rjson)
library(XML)
library(xml2)
library(plyr)
library(ggplot2)
library(dplyr)
library(maps)
library(ggmap)
# install.packages("gridExtra")


fs <- gridfs(db = "MS", url = "mongodb+srv://msds_user:msds@cluster0-bqyhe.gcp.mongodb.net/", prefix = "fs",options = ssl_options())

fs$upload("book.html")
```

# Collection  {.tabset .tabset-fade .tabset-pills}
## Collect Data
```{r}
 url <- "https://www.booksamillion.com/search?id=7523317361322&query=&filter=product_type%3Abooks"
   first_page <- read_html(url)
   
   # Read Title
   Title <- html_nodes(first_page,'.title') %>%   html_text()  %>%  str_trim() %>%    unlist() 
   # Read Author
   Author <- html_nodes(first_page,'.list') %>%   html_nodes('.byline') %>% html_text()  %>%  str_trim() %>%    unlist() 
  
   finaldf <- data.frame(title = Title,Auth = Author)
   
   #...... separate ...... Author to Authors and ISBN
   finaldf <- separate(finaldf,Auth,c("Author","ISBN"),sep = "ISBN")
   
   #...... separate ...... ISBN to REL_Date and ISBN  , as they are separated by "/"  
   finaldf <- separate(finaldf,ISBN,c("ISBN","REL_Date"),sep = "\\/")
   
   #...... separate ......Author to Author1 and Author2  , as they are separated by ","
   finaldf <- separate(finaldf,Author,c("Author1","Author2"),sep = ",")
  
   #.......trimws.......
   finaldf$Author1 <- trimws(str_sub(finaldf$Author1,3,-1L))
   finaldf$Author2 <- trimws(finaldf$Author2)
```

## Build CSV File 
```{r}
 #.......Write CSV File .....
    write.csv(finaldf,"book.csv")
   
```

## Save to Mongo
```{r}
 fs$upload("book.csv")
```


# Create File  {.tabset .tabset-fade .tabset-pills}
## XML From Data  {.tabset .tabset-fade .tabset-pills}
### Mannual Sample 
```{r}
# Reading Book xml from local directory 
readBookXML <- read_lines("book.xml")
print(readBookXML)
```

### Create XML By R
```{r}
prefix.xml <- "<?xml version='1.0' encoding='UTF-8'?><root>
                  <element>
                    <title> 'MS DS Work'</title>
                    <author> 'Rajwant Mishra'</author>
                   </element>   
               </root>"

# DUMMY DATA FRAME
df <- tibble(title= finaldf$title,Author1 = finaldf$Author1,Author2 = finaldf$Author2,ISBN = finaldf$ISBN,REL_Date = finaldf$REL_Date)

# BUILD XML TREE
doc = xmlTreeParse(prefix.xml, useInternalNodes = T)     # PARSE STRING
root = xmlRoot(doc)                                      # FIND ROOT

bookNode = newXMLNode("book", parent=root)           # ADD TO ROOT
xmlAttrs(bookNode) = c(type = "web")              # ADD ATTRIBUTE
 # pagesNode = newXMLNode("Element", parent=bookNode)       # ADD TO REPORT

for (i in 1:nrow(df)){
  eleNode = newXMLNode("Element", parent=bookNode)        # ADD PAGE FOR EACH RECORD
  xmlAttrs(eleNode) = c(ID = i) 
  # for (j in 1:ncol(df)){
    newXMLNode("title", df$title[i], parent=eleNode)  # ADD COL/ROW VALUE
    newXMLNode("author1", df$Author1[i], parent=eleNode)  # ADD COL/ROW VALUE
    newXMLNode("author2", df$Author2[i], parent=eleNode)  # ADD COL/ROW VALUE
     newXMLNode("ISBN", df$ISBN[i], parent=eleNode)  # ADD COL/ROW VALUE
     newXMLNode("REL_Date", df$REL_Date[i], parent=eleNode)  # ADD COL/ROW VALUE
  # }  
}

# VIEW XML
print(doc)

```

### Save XML 
```{r}
saveXML(doc, file="bookRXml.xml")
```

***
## Create  JSON  {.tabset .tabset-fade .tabset-pills}
### Mannual Sample 
```{r}
# Local Sample JOSN File .
readBookJSON <- read_lines("book.json")
print(readBookJSON)
```

### Create JSON By R
```{r}

jsonlite::toJSON(df)


```

### Save JSON
```{r}
write_file(jsonlite::toJSON(df),"bookR.json")
```

***
## Create HTML  
### Mannual Sample 
```{r}
htmltools::includeHTML("book.html")
```

***
# Read   {.tabset .tabset-fade .tabset-pills}
## XML 
```{r}
XMLurl <- "https://raw.githubusercontent.com/Rajwantmishra/msds/master/607/week7/bookRXml.xml"
readBookXML <- read_xml("bookRXml.xml")
readBookXML <- read_xml(XMLurl)
print(readBookXML)
xbook <- xml_children(readBookXML)
xbook.element <- xml_children(xbook[2])
xml_children(xbook.element[1])

xml_path(xbook)
# -----
class(xml_find_all(readBookXML, ".//title"))


xml_title <- xml_find_all(xbook.element, ".//title")
xml_author1 <- xml_text(xml_find_all(readBookXML, ".//author1"))
xml_author2 <-xml_text(xml_find_all(readBookXML, ".//author2"))
xml_ISBN <- xml_text(xml_find_all(readBookXML, ".//ISBN"))
xml_REL_Date <-xml_text(xml_find_all(readBookXML, ".//REL_Date"))

xml_titleAll <- xml_text(xml_find_all(readBookXML, ".//title"))

ldply(xml_text(xml_children(xbook.element[1])))


x <- read_xml("<root id='1'><child id ='a' /><child id='b' d='b'/></root>")
xml_attr(x, "id")
xml_attr(x, "apple")
xml_attrs(xbook.element,"ID")

xml_children(xml_children(xbook[2]))


xml_find_first(xbook.element, ".//title")
xml_text(xml_find_all(xbook.element, ".//title"))

XML_Book <- tibble( title = unlist(xml_text(xml_title)), 
                    author = unlist(xml_author1),
                    author2 = unlist(xml_author2),
                    ISBN = unlist(xml_ISBN),
                    REL_Date = unlist(xml_REL_Date)
                    )

ldply(xml_text(xml_title))



datatable(XML_Book)




```

## JSON
```{r}

jsonURL <- "https://raw.githubusercontent.com/Rajwantmishra/msds/master/607/week7/bookR.json"

readbookJOSN <- read_file(jsonURL)

jsonlite::fromJSON(readbookJOSN)


#LOCAL READ 

readbookJOSN <- read_file("book.json")
jsonlite::fromJSON(readbookJOSN)
```

## HTML
```{r}
bookHTML <- read_html("book.html")

# ------------------Method 1
bookHTML1 <- read_html("book.html")


tbls_ls <- bookHTML1 %>%
        html_nodes("table") %>%
        .[1] %>%
        html_table(fill = TRUE)

str(tbls_ls)


# ------------------Method 2
readHTMLTable("book.html")[[1]]



```

## Mongo DB
```{r}
fs$download('book.csv','bookMONGO.csv')
bookMongoCSV <- read_csv("bookMONGO.csv")
datatable(bookMongoCSV)
```

