---
title: "607 Week 3 Assignment"
author: "Rajwant Mishra"
date: "February 11, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Please deliver links to an R Markdown file (in GitHub and rpubs.com) with solutions to problems 3 and 4 from chapter 8 of Automated Data Collection in R.  Problem 9 is extra credit.  You may work in a small group, but please submit separately with names of all group participants in your submission.

Here is the referenced code for the introductory example in #3:

 raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

Due end of day Sunday.



```{r}

library(tidyverse)
library(lubridate)
library(stringr)
raw <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

name <-   as.data.frame(str_split(raw,"555"))
names(name) <- c("NAME")

name <- str_replace_all(name$NAME,
                        "-|[\\d]|\\(|\\)|\\.","")
trimws(name[name!=""])




# Here, apply gives each row to any, which checks if the expression x=="" (which is itself a vector) is true for any of the elements and if so, it returns TRUE. The whole apply expression thus returns a vector of TRUE/FALSE statements, which are negated with !. This can then be used to subset your data.
name <- as.data.frame(name)
name <- name[!apply(name, 1, function(x) any(x=="")),] 
name

name2 <- unlist(str_extract_all(raw, "[[:alpha:]., ]{2,}"))
name2

fn <- unlist(str_extract_all(raw, "[[:alpha:]., ]{2,}"))


fn <- unlist(str_extract_all(raw, "[[:alpha:].?, ]{2,}"))

fn
```

```{r}
str_extract_all(raw.data,"\\d?(\\d{3})?")

p<- unlist(str_extract_all(raw.data, "\\(?(\\d{3})?\\)?(-| )?\\d{3}(-| )?\\d{4}"))

digit

example.obj <- c("1. A small sentence. - 2. Another tiny sentence.")

unlist(str_extract_all(example.obj, "[[:punct:]ABC]"))
unlist(str_extract_all(example.obj, "[[:punct:]A-Ca-c]"))
unlist(str_extract_all(example.obj, "[[:alnum:]]|[[:punct:]]"))

unlist(str_extract_all(example.obj, "s[[:alpha:]]{5}"))

unlist(str_extract_all(example.obj, "s[[:alpha:]]{5}"))
unlist(str_extract_all(example.obj, "A.+?sentence"))

unlist(str_extract_all(example.obj, fixed(".")))

unlist(str_extract_all(example.obj, fixed(".")))
unlist(str_extract_all(example.obj, "\\."))

unlist(str_extract_all(example.obj, "(\\D){1,10}"))
unlist(str_extract_all(example.obj, "(\\w){1,8}"))

unlist(str_extract_all(example.obj, "(\\w){3}"))
unlist(str_extract_all(example.obj, "\\w+"))


unlist(str_extract_all(example.obj, "\\<s"))
unlist(str_extract_all(example.obj, "e\\b"))

str_extract(example.obj, "(\\<[b-z]+\\>).+?\\1")


str_extract(example.obj, "\\s+")

```

```{r}
raw.data <- "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev.Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr.Julius Hibbert"

unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
unlist(str_extract_all(raw.data, "[[:alpha:] .,]{2,}"))

unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))

unlist(str_extract_all(raw.data, "[^[:alpha:]-]{3,}"))
unlist(str_extract_all(raw.data, "\\(?(\\d{3})?\\)?(-| )?\\d{3}(-| )?\\d{4}"))
unlist(str_extract_all(raw.data, "\\(?(\\d{3})?\\)?"))
unlist(str_extract_all(raw.data, "\\(?(\\d{3})?\\)?(-| )?\\d{3}(-| )?\\d{4}"))
```
```{r}
agrep("Barack Obama", "Michelle Obama", max.distance = list(all = 6))
make.unique(c("a", "b", "a", "c", "b", "a"))
pmatch(c("and this", "and that", "and these", "and those"), char.vec)

```

```{r}
library(XML)
# download file
if(!file.exists("listOfSimpsonsEpisodes.html")){
link <- "http://en.wikipedia.org/wiki/List_of_The_Simpsons_episodes"
download.file(link, "listOfSimpsonsEpisodes.html", mode="wb")
}

tables <- readHTMLTable("listOfSimpsonsEpisodes.html",header=T, stringsAsFactors=F)

length(tables)
tables[[3]]

tmpcols <- names(tables[[3]])
for(i in 3:19){
tmpcols <- intersect(tmpcols, names(tables[[i]]))
}



episodes <- NULL
for(i in 3:19){
episodes <- rbind(episodes[,tmpcols],tables[[i]][,tmpcols])
}
for(i in 1:dim(episodes)[2]){
Encoding(episodes[,i]) <- "UTF-8"
}
names(episodes) <- c("pnr", "nr", "title", "directedby","Writtenby", "airdate", "productioncode")
save(episodes,file="episodes.Rdata")
#Let us load the table containing all the Simpsons

```
```{r}
con2 <- dbConnect(RMySQL::MySQL(), dbname = "flights", host="localhost", user="root",password= "")
query <- "SELECT * FROM movies_review"

tab1 <- dbSendQuery(con2,query)
suppressWarnings(rm(movies_review ))
movies_review <- dbFetch(tab1)
query <- "SELECT * FROM movies_master"

tab1 <- dbSendQuery(con2,query)
movies_master <- dbFetch(tab1)
#disconenct DB
dbDisconnect(con2)

glimpse(movies_review)
glimpse(movies_master)

grep("Bad",movies_master$Movie_Name[1:3], value=T)

grep("Bad",movies_master$Movie_Name[1:3])

grepl("Bad",movies_master$Movie_Name[1:10])


grep("ar",movies_master$Movie_Name[1:10], value=T)
grepl("ar",movies_master$Movie_Name[1:10])
movies_master$Movie_Name
grepl("Bad",movies_master$Movie_Name[1:10])
grepl("Star",movies_master$Movie_Name[1:10])

indicies <- sapply(c("Truth","Dare"),grepl, movies_master$Movie_Name,
ignore.case = FALSE, perl = FALSE,
fixed = FALSE, useBytes = FALSE)

index <- apply(indicies, 1, all) # Retrun strict and match 


indicies <- sapply(c("Bad","Star"),grepl, movies_master$Movie_Name,
ignore.case = FALSE, perl = FALSE,
fixed = FALSE, useBytes = FALSE)
index <- apply(indicies, 1, any)  # Retrun any of the match 

grepall <- function(pattern, grepl, x,
ignore.case = FALSE, perl = FALSE,
fixed = FALSE, useBytes = FALSE,
value=FALSE, logic=FALSE){
  # apply grepl() and all()
indicies <- sapply(pattern, grepl, x,
ignore.case, perl, fixed, useBytes)
}



shiny_demo("Loterry")



```

```{r}
Sys.getlocale()
small.frogs <- "Sm°a grodorna, sm°a grodorna ¨ar lustiga att se."
small.frogs

Encoding(small.frogs)

small.frogs.utf8 <- iconv(small.frogs, from = "windows-1252",
to = "UTF-8")

Encoding(small.frogs.utf8)
small.frogs.utf8

Encoding(small.frogs.utf8) <- "windows-1252"
small.frogs.utf8

iconvlist()

```


```{r}


library(RCurl)

enc.test <- getURL("http://www.sciencemag.org/")
unlist(str_extract_all(enc.test, "<meta.+?>"))

unlist(str_extract_all(enc.test, "<meta.+?>"))
```



```{r}

unlist(str_extract_all(raw, "[[:alpha:]., ]{2,}"))
p<- unlist(str_extract_all(raw.data, "\\(?(\\d{3})?\\)?(-| )?\\d{3}(-| )?\\d{4}"))


rawdata<-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
raw.data 
names <- unlist(str_extract_all(rawdata, "[[:alpha:]., ]{2,}"))

names

# [1] "Moe Szyslak"          "Burns, C. Montgomery" "Rev. Timothy Lovejoy" "Ned Flanders"        
# [5] "Simpson, Homer"       "Dr. Julius Hibbert" 



```

```{r}

unlist(str_extract_all(names,"[[:alpha:]]{2,}|[[:alpha:]. ?]{2,}|[.?[:alpha:] ]{2,}"))

unlist(str_extract_all(names,"[[:alpha:]]{2,}"))

unlist(str_extract_all(names,"[[:alpha:]]{2,}|[[:alpha:] .?[:alpha:]]{2,}|[[:alpha:]. ?]{2,} "))

unlist(str_extract_all(names,"[[:alpha:]. ]{3,}"))

 unlist(str_extract_all(names,"([[:alpha:]. ]{2,})?"))
first


str_extract_all(c("Dr. Julius Hibbert","Rev. Timothy   Lovejoy"),"[[:alpha:].?{1,3}]{2,}")


unlist(lapply(strsplit(names, " "), function(x) { return(x[length(x)-1]) }))

# Moe           Szyslak         
# Burns         C. Montgomery 
# 
# Ned           Flanders      
# Simpson,      Homer
# Dr. Julius    Hibbert


strings = c("12 Jun 2002", " 8 September 2004 ", "22-July-2009 ",
"01 01 2001", "date", "02.06.2000",
"xxx-yyy-zzzz", "$2,600")
# date pattern (month as text)
dates = "([0-9]{1,2})[- .]([a-zA-Z]+)[- .]([0-9]{4})"
str_match(strings, dates)

str_match(names, "[[:alpha:]]{2,}|[[:alpha:]. ?]{2,}")
```




```{r}

# WORKING 
grepall <- function(pattern, x,
ignore.case = FALSE, perl = FALSE,
fixed = FALSE, useBytes = FALSE,
value=FALSE, logic=FALSE){
  
  # error and exception handling
if(length(pattern)==0 | length(x)==0){
warning("Length of pattern or data equals zero.")
return(NULL)
}
# apply grepl() and all()
indicies <- sapply(pattern, grepl, x,
ignore.case, perl, fixed, useBytes)
index <- apply(indicies, 1, all)
# indexation and return of results
if(logic==T) return(index)
if(value==F) return((1:length(x))[index])
if(value==T) return(x[index])
}


#-----------------------------Dispaly Name -------------------------------------------
rawdata<-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

names <- unlist(str_extract_all(rawdata, "[[:alpha:]., ]{2,}"))

names


#-----------------------------Dispaly 1st and Last name  -------------------------------------------
Title <- NA
Title[grepall("Dr.",names)] <- "Dr."
Title[grepall("Rev.",names)] <- "Rev."

tName <- trimws(str_replace_all(names,"Rev.|Dr.",""))
FLName <- trimws(unlist(str_extract_all(tName,"[[:alpha:]]{2,}|[[:alpha:]. ?]{2,}|[.?[:alpha:] ]{2,}",1)))
colnames(FLName) <- c("First Name","Last Name")
data.frame(Title,"Full Name" = tName,FLName)

#-----------------------------HAS Title (Rev. or Dr.) -------------------------------------------
data.frame(names,Title,"Has_Title"= (grepl(c("Dr."),names)|grepl(c("Rev."),names)))

#-----------------------------HAS 2nd Name----------------------------------------------------------
data.frame("Raw Name " = names, "Full_Name" = tName,"Sec_Name" = ifelse(str_count(tName,"[[:alpha:]]+")>2,"YES","No"))

#--------------------------------------------------------------------------------------


unlist(str_extract_all(names,"[[:alpha:]]{1,3}"),1)
unlist(str_extract_all(names,"[[:alpha:]]{2,}"))
unlist(str_extract_all(names,"\\w.{2,}"))

# Moe           Szyslak         
# Burns         C. Montgomery 
# 
# Ned           Flanders      
# Simpson,      Homer
# Dr. Julius    Hibbert
# WORKING  END
```




```{r}

#-----------------------------------------------------------------

grepl(c("Dr."),names)
grepl(c("Rev."),names)
data.frame(names,"DR." = grepl(c("Dr."),names),"Rev." = grepl(c("Rev."),names))



#-----------------------------------"Rev.","Tim"-------------------------------
indicies <- sapply(c("Rev.","Tim"),grepl, names,
ignore.case = FALSE, perl = FALSE,
fixed = FALSE, useBytes = FALSE)

index <- apply(indicies, 1, all) # Retrun strict and match 


#------------------------------------------------------------------------------
# Has 2nd Name 
str_count("asas asasdsa asdasdsad .dsafdfd",pattern = ".")
data.frame(names,ifelse(str_count(names,"[[:alpha:]]+")>2,"YES","No"),"DR." = grepl(c("Dr."),names),"Rev." = grepl(c("Rev."),names))

data.frame(names,str_detect(names,", ?"),"DR." = grepl(c("Dr."),names),"Rev." = grepl(c("Rev."),names))

```

```{r}


```







```{r}
# (a) [0-9]+\\$
# (b) \\b[a-z]{1,4}\\b
# (c) .*?\\.txt$
# (d) \\d{2}/\\d{2}/\\d{4}
# (e) <(.+?)>.+?</\\1>
example.obj <- "1. A small sentence. - 2. Another tiny sentence."
unlist(str_extract_all(example.obj, "[a-z]{1,4}"))

a <- c("0121210121$ 3423423 1232$ 0932$ 444")
str_extract_all(a,"[0-9]+\\$")
# Would retrun only number from 0-9 in contuinues ending with $ at the end.

b<-  "nice verynice FIIVE SIIIXX ONE TWO THREE FOUR NICE TINY MANGO msds msdsd 0932$ 444 smal four."
unlist(str_extract_all(b, "\\b[a-z]{1,4}\\b"))
# Only returns small letter word  of exact length 4

# (c) .*?\\.txt$
c<- c("one.txt","two.*.txt","three.*txt$" , "four.*.txt$", "fine.*.tx" ,"Abcd MSDS max.txt  dot.*txt  onemore.*.txt")
unlist(str_extract_all(c, ".*?\\.txt$"))

# data which are like <name>.txt , <name>.?*txt or any text ending ".txt"" will be retrun from this .




# (d) \\d{2}/\\d{2}/\\d{4}
d<- c("12/12/201","1/1/2012","01/12/2019", "00/0/2019","12/02/2019")
unlist(str_extract_all(d, "\\d{2}/\\d{2}/\\d{4}"))
# strin starting with number , {2}  say only 2 number , then "/" and again 2 number , then "/" and then 4 number.

# (e) <(.+?)>.+?</\\1>

# uses backreferencing to return any string that starts with a ``<text>`` and ends with ``</text>``

e <- "<meta>MSDS CLASS 607</meta> <ol><li>Assignment</li><li>3e</li></ol>"
unlist(str_extract_all(e, '<(.+?)>.+?</\\1>'))

```




```{r}



ddd<- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"

is.locale(ddd)
iconv(ddd, from = "windows-1252", to = "UTF-8")

Encoding(ddd)

Encoding("I am rajwant")


str_extract_all(ddd,"\\d+")
str_extract_all(ddd,"\\w")
str_extract_all(ddd,"\\w[[:punct:]]")
str_extract_all(ddd,"[[:upper:].]")

unlist(str_extract_all(ddd,"[A-Z.]"))

paste0(unlist(str_extract_all(ddd,"[A-Z.]")),collapse = "")

str_split(paste0(unlist(str_extract_all(ddd,"[A-Z.]")),collapse = ""),
          "\\.",simplify = TRUE)
#-------------------------------------------------------END -----------------------------------

str_extract_all(ddd,"\\w[[:punct:]]")
str_extract_all(ddd,"\\d[[A-Z]]")


unlist(str_extract_all(ddd, '[^[a-z]|[0-9]]'))


```

















