---
title: "607 Assignment Week3"
author: "Rajwant Mishra"
date: "February 15, 2019"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    highlight: tango
---
# Question {.tabset .tabset-fade .tabset-pills}

Please deliver links to an R Markdown file (in GitHub and rpubs.com) with solutions to problems 3 and 4 from chapter 8 of Automated Data Collection in R.  Problem 9 is extra credit.  You may work in a small group, but please submit separately with names of all group participants in your submission.

Here is the referenced code for the introductory example in #3:


```{r include=FALSE}

suppressWarnings(library(tidyverse))
suppressWarnings(library(stringr))
suppressWarnings(library(DT))
suppressWarnings(library(lubridate))

```


# Working {.tabset .tabset-fade .tabset-pills}

> raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

## Question 1

1. Copy the introductory example. The vector name stores the extracted names.
R> name
[1] "Moe Szyslak" "Burns, C. Montgomery" "Rev. Timothy Lovejoy"
[4] "Ned Flanders" "Simpson, Homer" "Dr. Julius Hibbert"

```{r}
# WORKING 


#-----------------------------Dispaly Name -------------------------------------------
rawdata<-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

names <- unlist(str_extract_all(rawdata, "[[:alpha:]., ]{2,}"))

names

```

## Question 2
2. Use the tools of this chapter to rearrange the vector so that all elements conform to
the standard first_name last_name.

* Moe           Szyslak         
* Burns         C. Montgomery 
* Ned           Flanders      
* Simpson,      Homer
* Dr. Julius    Hibbert


```{r}
#-------------------Dispaly 1st and Last name  --------------------

#-------------------------
# Target to acheive
#First Name  || Last Name |
#-------------------------
# Moe           Szyslak         
# Burns         C. Montgomery 
# 
# Ned           Flanders      
# Simpson,      Homer
# Dr. Julius    Hibbert
#-------------------------

#-------FM which returns postion of maching string in vector.
grepall <- function(pattern, x,
ignore.case = FALSE, perl = FALSE,
fixed = FALSE, useBytes = FALSE,
value=FALSE, logic=FALSE){
  
  # error and exception handling
if(length(pattern)==0 | length(x)==0){
warning("Length of pattern or data equals zero.")
return(NULL)
}
# apply grepl() and all()
indicies <- sapply(pattern, grepl, x,
ignore.case, perl, fixed, useBytes)
index <- apply(indicies, 1, all)
# indexation and return of results
if(logic==T) return(index)
if(value==F) return((1:length(x))[index])
if(value==T) return(x[index])
}

#------End of FM 

Title <- NA
Title[grepall("Dr.",names)] <- "Dr."
Title[grepall("Rev.",names)] <- "Rev."

tName <- trimws(str_replace_all(names,"Rev.|Dr.",""))
FLName <- trimws(unlist(str_extract_all(tName,"[[:alpha:]]{2,}|[[:alpha:]. ?]{2,}|[.?[:alpha:] ]{2,}",1)))
colnames(FLName) <- c("First Name","Last Name")
datatable(data.frame(Title,"Full Name" = tName,FLName))

```

## Question 3

3. Construct a logical vector indicating whether a character has a title (i.e., Rev. and
Dr.).


```{r}

#-----------------------------HAS Title (Rev. or Dr.) -------------------------------------------
data.frame(names,Title,"Has_Title"= (grepl(c("Dr."),names)|grepl(c("Rev."),names)))

# OPTION 2 : --------------
# Look for 2/3 character starting with Caps and followed by period ---------------------------- 
data.frame(names,Title,"Has_Title"=
str_detect(names,"\\b[A-Z]{1}[a-z]{1,2}\\."))


```

## Question 4

4. Construct a logical vector indicating whether a character has a second name.

```{r}
#-----------------------------HAS 2nd Name----------------------------------------------------------
data.frame("Raw Name " = names, "Full_Name" = tName,
           "Sec_Name" = ifelse(str_count(tName,"[[:alpha:]]+")>2,"TRUE","FALSE"))

#--------------------------------------------------------------------------------------

```

* Some  other Test

```{r}

unlist(str_extract_all(names,"[[:alpha:]]{1,3}"),1)
unlist(str_extract_all(names,"[[:alpha:]]{2,}"))
unlist(str_extract_all(names,"\\w.{2,}"))


# WORKING  END
```


 
## Question 5
 
 Describe the types of strings that conform to the following regular expressions and
construct an example that is matched by the regular expression.

+ (a) [0-9]+\\$
+ (b) \\b[a-z]{1,4}\\b
+ (c) .*?\\.txt$
+ (d) \\d{2}/\\d{2}/\\d{4}
+ (e) <(.+?)>.+?</\\1>

<details>
  <summary> Answer `(a) [0-9]+\\$`</summary>
  
  > Would retrun only number from 0-9 in contuinues ending with $ at the end.
  
```{r}
a <- c("0121210121$ 3423423 1232$ 0932$ 444")
str_extract_all(a,"[0-9]+\\$")

```
  
</details>
***

<details>
  <summary>Answer `(b) \\b[a-z]{1,4}\\b`</summary>
  
  > Only returns small letter word  of exact length 4.

```{r}
b<-  "nice verynice FIIVE SIIIXX ONE TWO THREE FOUR NICE TINY MANGO msds msdsd 0932$ 444 smal four."
unlist(str_extract_all(b, "\\b[a-z]{1,4}\\b"))


```

</details>
***

<details>
  <summary>Answer `(c) .*?\\.txt$` . </summary>
  
  > data which are like <name>.txt , <name>.?*txt or any text ending ".txt"" will be retrun from this .

```{r}
c<- c("one.txt","two.*.txt","three.*txt$" , "four.*.txt$", "fine.*.tx" ,"Abcd MSDS max.txt  dot.*txt  onemore.*.txt")
unlist(str_extract_all(c, ".*?\\.txt$"))

```

</details>
***

<details>
  <summary>Answer ` (d) \\d{2}/\\d{2}/\\d{4}` </summary>
  
  > string starting with number , {2}  say only 2 number , then "/" and again 2 number , then "/" and then 4 number.
  
```{r}
d<- c("12/12/201","1/1/2012","01/12/2019", "00/0/2019","12/02/2019")
unlist(str_extract_all(d, "\\d{2}/\\d{2}/\\d{4}"))

```

</details>
***

<details>
  <summary>Answer `(e) <(.+?)>.+?</\\1> `</summary>
  
  > Uses backreferencing to return any string that starts with a ``<text>`` and ends with ``</text>``.
  
```{r}
e <- "<meta>MSDS CLASS 607</meta> <ol><li>Assignment</li><li>3e</li></ol>"
unlist(str_extract_all(e, '<(.+?)>.+?</\\1>'))


```

</details>
***

## Challange 6

The following code hides a secret message. Crack it with R and regular expressions.
Hint: Some of the characters are more revealing than others! The code snippet is also
available in the materials at www.r-datacollection.com.

  > clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr

> Answer is  "CONGRATULATIONS.YOU.ARE.A.SUPERNERD"
```{r}



ddd<- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"


iconv(ddd, from = "windows-1252", to = "UTF-8")

Encoding(ddd)

Encoding("I am rajwant")


str_extract_all(ddd,"\\d+")
str_extract_all(ddd,"\\w")
str_extract_all(ddd,"\\w[[:punct:]]")
str_extract_all(ddd,"[[:upper:].]")

unlist(str_extract_all(ddd,"[A-Z.]"))

paste0(unlist(str_extract_all(ddd,"[A-Z.]")),collapse = "")

str_split(paste0(unlist(str_extract_all(ddd,"[A-Z.]")),collapse = ""),
          "\\.",simplify = TRUE)

```
#-------------------------------------------------------END -----------------------------------

***
***
***

```{r}
str_extract_all(ddd,"\\w[[:punct:]]")
str_extract_all(ddd,"\\d[[A-Z]]")


unlist(str_extract_all(ddd, '[^[a-z]|[0-9]]'))

```


## Some Other Test

```{r}

#-----------------------------------------------------------------

grepl(c("Dr."),names)
grepl(c("Rev."),names)
data.frame(names,"DR." = grepl(c("Dr."),names),"Rev." = grepl(c("Rev."),names))



#-----------------------------------"Rev.","Tim"-------------------------------
indicies <- sapply(c("Rev.","Tim"),grepl, names,
ignore.case = FALSE, perl = FALSE,
fixed = FALSE, useBytes = FALSE)

index <- apply(indicies, 1, all) # Retrun strict and match 


#------------------------------------------------------------------------------
# Has 2nd Name 
str_count("asas asasdsa asdasdsad .dsafdfd",pattern = ".")
data.frame(names,ifelse(str_count(names,"[[:alpha:]]+")>2,"YES","No"),"DR." = grepl(c("Dr."),names),"Rev." = grepl(c("Rev."),names))

data.frame(names,str_detect(names,", ?"),"DR." = grepl(c("Dr."),names),"Rev." = grepl(c("Rev."),names))
```