---
title: "607 Assignment 2"
author: "Rajwant Mishra"
date: "February 10, 2019"
output:
  html_document:
    df_print: paged
    
    toc_float: true
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Plan to scrap data from [here](https://www.imdb.com/list/ls026612019/)

# Loading Package 

***
library(tidyverse)  

    # Parsing of HTML/XML files  
    library(rvest)    

    # String manipulation
    library(stringr)   

    # Verbose regular expressions
    #install.packages("rebus")
    library(rebus)     

    # Eases DateTime manipulation
    library(lubridate)

    library(DT)
***

```{r include=FALSE}
# For SQL 
# install.packages("RSQLite")
library(RSQLite)
# General-purpose data wrangling
    library(tidyverse)  

    # Parsing of HTML/XML files  
    library(rvest)    

    # String manipulation
    library(stringr)   

    # Verbose regular expressions
    #install.packages("rebus")
    library(rebus)     

    # Eases DateTime manipulation
    library(lubridate)

    library(DT)

```


# {.tabset .tabset-fade .tabset-pills}

## Scrapping Function

* Reading only Rating , Title , Username and content of comments 

```{r}
## COllection of all the Function Needed 

 Final_Review <- NA

# Get Movie Name from Header
Mname <- function(html){
      html %>% 
        # The relevant tag
        html_nodes('.parent') %>%      
        html_text() %>% 
        # Trim additional white space
        str_trim() %>%                       
        # Convert the list into a vector
        unlist()                             
}


# Rating 



rating <- function(html){
      html %>% 
        # The relevant tag
        html_nodes('.rating-other-user-rating') %>%      
        html_text() %>% 
        # Trim additional white space
        str_trim() %>%                       
        # Convert the list into a vector
        unlist()                             
}



# Comment and Title 

mtitle <- function(html){
  
  if (!is.na(html_node(first_page,'.ipl-ratings-bar')))(
      html %>% 
        # The relevant tag
        html_nodes('.lister-item-content .title') %>%      
        html_text() %>% 
        # Trim additional white space
    map(1) %>%
        str_trim() %>%                       
        # Convert the list into a vector
        unlist()  )                           
}

# html_nodes(first_page,'.ipl-ratings-bar')
# COntributor Name 

mrname <- function(html){
   if (!is.na(html_node(first_page,'.ipl-ratings-bar')))(
      html %>% 
        # The relevant tag
        html_nodes('.display-name-link') %>%      
        html_text() %>% 
        # Trim additional white space
   
        str_trim() %>%                       
        # Convert the list into a vector
        unlist()  
   )
}



#display-name-date
#Desc .lister-item-content .content .text show-more__control

mdesc <- function(html){
   if (!is.na(html_node(first_page,'.ipl-ratings-bar')))(
      html %>% 
        # The relevant tag
        html_nodes('.content .text') %>%      
        html_text() %>% 
        # Trim additional white space
   
        str_trim() %>%                       
        # Convert the list into a vector
        unlist() 
   )
}

## End OF COllection Function 




readAllAttribute<- function(html){
  getMoviewName <- Mname(html)
  str_split(getMoviewName,"\n") # Got the moview name 
 temp_movieName <- trimws(str_split(getMoviewName,"\n",simplify = TRUE))
  # Read Rating 
  rating <- rating(html)
  
  # Comment Title 
  title<- mtitle(html)
  
  # COntributor Name 
  name<- mrname(html)
  
  #Comment Content
  desc<- mdesc(html)
  # Retrun Final Data 
 suppressWarnings(rm(Final_Review))
 
  Final_Review <- data.frame(rating,desc[1:length(rating)],title[1:length(rating)],name[1:length(rating)])
  
  fm_movie_name <-  temp_movieName[1,1]
 fm_movie_year <-  str_replace_all(temp_movieName[1,2],"\\(|\\)|[A-Z]","")
 
 print ("----------------------------------------------------")
 print(fm_movie_name)
 print ("----------------------------------------------------")
 updateDB (fm_movie_name,fm_movie_year , Final_Review )

}



```


## DB Function 

* Connect to DB 
* Setup table 
* Update record function 
* Data wrangling to Replace special char with scapce sequence  or  blank


```{r}
CheckDB <- function() {
  con2 <- dbConnect(RMySQL::MySQL(), dbname = "MSDS2019", host="148.72.58.145", user="MSDS2019",password= "!S(Ue1&?scWA")
  # con2 <- dbConnect(RMySQL::MySQL(), dbname = "flights", host="localhost", user="root",password= "")

# DRop Table if Present 
if(dbExistsTable(con2, "movies_master")){
  dbRemoveTable(con2, "movies_review")
    dbRemoveTable(con2,"movies_master")
  
  }
 
query <- "CREATE TABLE `movies_master` (   `ID` INT NOT NULL AUTO_INCREMENT,  `Movie_Name` VARCHAR(45) NULL,   `Year` YEAR NULL,   PRIMARY KEY (`ID`))"


tab1 <- dbSendQuery(con2,query)
tab1data <- dbFetch(tab1)

#Create another table to hold review 

query <- "CREATE TABLE `movies_review` 
(  `ID` INT NOT NULL AUTO_INCREMENT,  
`Movie_ID` INT NOT NULL,  
`User_Name` VARCHAR(45) NULL,  
`Rating` INT NULL,  
`Title` VARCHAR(45) NULL,  
`Content` VARCHAR(1000) NULL,
PRIMARY KEY (`ID`, `Movie_ID`),  
 CONSTRAINT `ID`    FOREIGN KEY (`Movie_ID`)    
 REFERENCES `flights`.`movies_master` (`ID`)    
 ON DELETE NO ACTION     ON UPDATE CASCADE)"

tab1 <- dbSendQuery(con2,query)
tab1data <- dbFetch(tab1)

# Close COnnection
dbDisconnect(con2)
  
}

updateDB <- function(movie_name,myear,reviews){
# 
#   con2 <- dbConnect(RMySQL::MySQL(), dbname = "flights", host="localhost", user="root",password= "")
  con2 <- dbConnect(RMySQL::MySQL(), dbname = "MSDS2019", host="148.72.58.145", user="MSDS2019",password= "!S(Ue1&?scWA")
 
  # Update table with Movies name 
query <- sprintf("insert into movies_master (Movie_Name,Year) values('%s',%s)",movie_name,myear)
  print (query)
tab1 <- dbSendQuery(con2,query)
tab1data <- dbFetch(tab1)

# Get movie key to update review 
query <- sprintf("select  ID from movies_master  where Movie_Name ='%s' and Year = %s limit 1",movie_name,myear)
  
tab1 <- dbSendQuery(con2,query)
tab1data <- dbFetch(tab1)
movie_ID <- tab1data$ID
# update REview 



for (n in  1:dim(reviews)[1])
{
  temprating <- str_split(reviews$rating,"/",n=2,simplify = TRUE)[n,1]
# # Replace and a all special char with scapce sequence  word  # . \ | ( ) [ { ^ $ * + ?   replace
tempdesc <- str_replace_all(reviews$desc[n],"\\n|\\(|\\)|\\'|\\:|\\--|\\||\\*","")
temptitle <-  str_replace_all(reviews$title[n],"\\n|\\(|\\)|\\'|\\:|\\--|\\||\\*","")
tempname <- str_replace_all(reviews$name[n],"\\n|\\(|\\)|\\'|\\:|\\--|\\||\\*","")

 query<-  sprintf("insert into movies_review (Movie_ID,User_name,Title,Content,rating) values(%s,'%s','%s','%s',%s)",movie_ID,tempname, temptitle ,tempdesc,temprating )
 print(query)
 tab1 <- dbSendQuery(con2,query)
 
tab1data <- dbFetch(tab1)
}


# Close COnnection
dbDisconnect(con2)
  
}

```


## Main Task 

* Start scarping the DATA
* Update DB

```{r}
# Set the URL To scarp data of Reviews from 
#       ID| Movie Name |  Year |
#  Rev_ID | Movie ID | Title | Rating | Dec |

 url <-c('https://www.imdb.com/title/tt3203528/reviews?ref_=tt_urv',
          'https://www.imdb.com/title/tt4154756/reviews?ref_=tt_urv',
          'https://www.imdb.com/title/tt2231461/reviews?ref_=tt_urv',
          'https://www.imdb.com/title/tt6772950/reviews?ref_=tt_urv',
         'https://www.imdb.com/title/tt3606756/reviews?ref_=tt_urv',
          'https://www.imdb.com/title/tt1517451/reviews?ref_=tt_urv')
 

CheckDB()
for (n in 1:6){
  print (n)
  suppressWarnings(rm(first_page))
first_page <- read_html(url[n])
suppressWarnings(rm(getReview))
readAllAttribute(first_page)
}

```


## Data Display

* Read data from DB
* Disaply in R
* Data Wrangling in R

```{r}
# Database Operation 
# con2 <- dbConnect(RMySQL::MySQL(), dbname = "flights", host="localhost", user="root",password= "")

con2 <- dbConnect(RMySQL::MySQL(), dbname = "MSDS2019", host="148.72.58.145", user="MSDS2019",password= "!S(Ue1&?scWA")

query <- "SELECT * FROM movies_review"

tab1 <- dbSendQuery(con2,query)
suppressWarnings(rm(movies_review ))
movies_review <- dbFetch(tab1)

query <- "SELECT * FROM movies_master"

tab1 <- dbSendQuery(con2,query)
movies_master <- dbFetch(tab1)

datatable(movies_master)

table(movies_review$Movie_ID)
table(movies_review$Rating)

query <- "select Movie_ID,  avg(Rating) from movies_review group by Movie_ID"

tab1 <- dbSendQuery(con2,query)
movie_rating <- dbFetch(tab1)


#--------------------------------------------------------------------#
# Movie with 5+ rating 
query <- "select Movie_ID, count(rating) from movies_review  where rating > 5 group by movie_id "

tab1 <- dbSendQuery(con2,query)
movie_rating_5plus <- dbFetch(tab1)

#disconenct DB
dbDisconnect(con2)

# Check movie_rating_5plus by within R  
movie_rating_5plusr<-  as.data.frame(table (movies_review[which (movies_review$Rating>5),2]))

names(movie_rating_5plusr ) <- c("Movie_ID","count(rating)")

# Both data points are same.

#--------------------------------------------------------------------#

# Movie Rating by MOvie Name 

datatable(mutate(movie_rating, Name = movies_master[which(movies_master$ID==movie_rating$Movie_ID),2], Rating = movie_rating$`avg(Rating)` )[,c(1,3,4)],style = 'bootstrap') %>%
   formatStyle(
  'Movie_ID',
  backgroundColor = styleEqual(c(1, 2,3,4,5,6), c('gray', 'yellow',"blue","red","purple","maroon"),'white'))


#--------------------------------------------------------------------#

# Update Movie name in MOvie Review 
movies_review$name <- movies_review$Movie_ID
for( n in 1:length(movies_master$ID)){
movies_review$name<- str_replace_all(movies_review$name,paste0(movies_master$ID[n],collapse = ", "),movies_master$Movie_Name[n])

}




datatable(movies_review[,c(2,7,3,4,5,6)],style = 'bootstrap') %>%
   formatStyle(
  'Movie_ID',
  backgroundColor = styleEqual(c(1, 2,3,4,5,6), c('gray', 'yellow',"blue","red","purple","maroon"),'white')
 
  )


```

