---
title: "606 Assignment1 - Loading Data into a Data Frame"
author: "Rajwant Mishra"
date: "January 31, 2019"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Problem Statement 

---

<b >Your task </b>  

+ study the dataset and the associated description of the data (i.e. "data dictionary"). You may need
to look around a bit, but it's there! 

+ You should take the data, and create a data frame with a subset of the columns
in the dataset. 

+ You should include the column that indicates edible or poisonous and three or four other columns.
+ You should also add meaningful column names and replace the abbreviations used in the data-for example, in the appropriate column, "e" might become "edible."

+ Your deliverable is the R code to perform these transformation tasks.

---

#  Solution {.tabset .tabset-fade .tabset-pills}




## Data Source

+ [Source of Data](https://archive.ics.uci.edu/ml/datasets/mushroom)

+ [Data File](https://archive.ics.uci.edu/ml/machine-learning-databases/mushroom/)

+ [Data Desc](https://archive.ics.uci.edu/ml/machine-learning-databases/mushroom/agaricus-lepiota.names)

## About DataSet

    (a) Mushroom records drawn from The Audubon Society Field Guide to North
        American Mushrooms (1981). G. H. Lincoff (Pres.), New York: Alfred
        A. Knopf
    (b) Donor: Jeff Schlimmer (Jeffrey.Schlimmer@a.gp.cs.cmu.edu)
    (c) Date: 27 April 1987


## Loading Packages 
~~~~~~~

suppressWarnings(library(tidyverse))
suppressWarnings(library(stringr))
suppressWarnings(library(data.table))
library(plyr)
library(XML)
library(crayon)
library(lubridate)
library(rjson)
library(readxl)

~~~~~~~

```{r include=FALSE}

#install.packages("tidyverse")

suppressWarnings(library(tidyverse))
suppressWarnings(library(stringr))
suppressWarnings(library(data.table))
library(plyr)
library(XML)
library(crayon)
library(lubridate)
library(rjson)
library(readxl) 

```

# Load/Display Data {.tabset .tabset-fade .tabset-pills}

## Local Read


```{r}
setwd("C:\\Users\\951250\\Documents\\myR\\MS\\607")
workDir <- getwd()
filePath = paste0(workDir,"/data")
# fileName <- list.files(path=filePath)

# mushroom <- read_delim(paste0(filePath,"/","mushroom.data" ))
# coloumName <- c(" ")

mushroom_meta <- read_delim(paste0(filePath,"/","atr.txt"),delim=".",col_names = FALSE)

# using the Name from above tible to set the header of the mushroom dataset
mushroom <- read_delim(paste0(filePath,"/","mushroom.data" ),delim = ",",col_names = trimws(mushroom_meta$X2))


```

## Check Data

> Data of Mushsroom datset  `r head(mushroom) `

> Data of Masuhroom Dataset's Attributes 

```{r}

names(mushroom_meta) <- c("ID","Type","Value")
head(mushroom_meta[,c(2,3)] )



```


##  Replace Value

* Replace Header from Meta data
```{r}

head(mushroom)
mushroom <- mutate(mushroom,classes = ifelse(classes == "p", "poisonous", "edible"))

```

* Update Meaning in the Column

```{r}
mushroom$`cap-shape`<- revalue(mushroom$`cap-shape`,c(b="bell",c="conical",x="convex",f="flat",
                                  k="knobbed",s="sunken"))
mushroom$`cap-surface` <- revalue(mushroom$`cap-surface`,c(f="fibrous",g="grooves",y="scaly",s="smooth"))

mushroom$`cap-color` <- revalue(mushroom$`cap-color`,c(n = "brown" ,b ="buff", c="cinnamon", g= "gray" ,r ="green",p ="pink" ,u= "purple" ,e="red", w ="white", y= "yellow"))

head(mushroom[,c(1:4)])
glimpse(mushroom[,c(1:4)])

```


## Subset of Data

```{r}
# Data Subset
mushroom_edible <- subset(mushroom,select = c(1:5))

head(mushroom_edible)

```


***

# Thank You


