---
title: "Project_606"
author: "Rajwant Mishra"
date: "April 24, 2019"
output: html_document
---

```{r}
#  Final Project Format 
# 	The final report should be presented in more formal format. Consider your audience to be non data analysts. Fellow data analysts (i.e. students) will be able to access your R Markdown file for details on the analysis. Submit a Zip file with your R Markdown file, the HTML output, and any supplementary files (e.g. data, figures, etc.). You must address the five following sections:
# 
# Introduction: What is your research question? Why do you care? Why should others care?
# 
# Data: Write about the data from your proposal in text form. Address the following points:
# 
# Data collection: Describe how the data were collected.
# Cases: What are the cases? (Remember: case = units of observation or units of experiment)
# Variables: What are the two variables you will be studying? State the type of each variable.
# Type of study: What is the type of study, observational or an experiment? Explain how you've arrived at your conclusion using information on the sampling and/or experimental design.
# Scope of inference - generalizability: Identify the population of interest, and whether the findings from this analysis can be generalized to that population, or, if not, a subsection of that population. Explain why or why not. Also discuss any potential sources of bias that might prevent generalizability.
# Scope of inference - causality: Can these data be used to establish causal links between the variables of interest? Explain why or why not.
# Exploratory data analysis: Perform relevant descriptive statistics, including summary statistics and visualization of the data. Also address what the exploratory data analysis suggests about your research question.
# 
# Inference: If your data fails some conditions and you can't use a theoretical method, then you should use simulation. If you can use both methods, then you should use both methods. It is your responsibility to figure out the appropriate methodology.
# 
# Check conditions
# Theoretical inference (if possible) - hypothesis test and confidence interval
# Simulation based inference - hypothesis test and confidence interval
# Brief description of methodology that reflects your conceptual understanding
# Conclusion: Write a brief summary of your findings without repeating your statements from earlier. Also include a discussion of what you have learned about your research question and the data you collected. You may also want to include ideas for possible future research.
# 
```



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(DT)
library(stringr)
library(lubridate)
library(corrr)
library(psych)
library(readxl)
library("readr")


```


---
title: DATA 606 Data Project Proposal
author: 
---


```{r echo=FALSE}
# load data
workDir <- getwd()

filePath = paste0(workDir,"/Data")
g_max <- 1048576 
ctype = c("text","text","text","text","text","numeric","numeric","text","text","text","text","text","text","text")

 Q1_17 <-read_excel(path=paste0(filePath,"/","2017_Q1.xlsx"),sheet="Data",guess_max =g_max)
 Q2_17 <-read_xlsx(path=paste0(filePath,"/","2017_Q2.xlsx"),sheet="Data",guess_max =g_max)
 Q3_17 <-read_xlsx(path=paste0(filePath,"/","2017_Q3.xlsx"),sheet="DATA",guess_max =g_max)
 Q4_17 <-read_excel(path=paste0(filePath,"/","2017_Q4.xlsx"),sheet="DATA",guess_max =g_max)
 Q1_18 <-read_excel(path=paste0(filePath,"/","2018_Q1.xlsx"),sheet="Data",guess_max =g_max)
 Q2_18 <-read_excel(path=paste0(filePath,"/","2018_Q2.xlsx"),sheet="Data",guess_max =g_max)
 Q3_18 <-read_excel(path=paste0(filePath,"/","2018_Q3.xlsx"),sheet="Data",guess_max =g_max)
 Q4_18 <-read_excel(path=paste0(filePath,"/","2018_Q4.xlsx"),sheet="Data",guess_max =g_max)
 custmap <- read_excel(path=paste0(filePath,"/","custmap.xlsx"),col_types = c("text","text"))

 # Create Subset 
Q1_17 <- Q1_17[,c(2,3,4,5,6,7,8,9,10,14,15,16,17,18,19,20,21,22,25,26,27)]
Q2_17 <- Q2_17[,c(2,3,5,6,7,8,9,10,11,17,18,19,20,21,22,24,25,26,30,31,32)]
Q3_17 <- Q3_17[,c(1,2,4,5,6,7,8,9,10,16,17,18,19,20,22,23,24,25,29,30,31)]
Q4_17 <- Q4_17[,c(2,3,5,6,7,8,9,10,11,17,18,19,20,21,23,24,25,26,29,30,31)]
Q1_18 <- Q1_18[,c(1,2,4,5,6,7,8,9,10,16,17,18,19,20,22,23,24,25,29,30,31)]
Q2_18 <- Q2_18[,c(2,3,5,6,7,8,9,10,11,17,18,19,20,21,23,24,25,26,30,31,32)]
Q3_18 <- Q3_18[,c(2,3,5,6,7,8,9,10,11,18,19,20,21,22,24,25,26,27,31,32,33)]
Q4_18 <- Q4_18[,c(2,3,5,6,7,8,9,10,11,18,19,20,21,22,24,25,26,27,31,32,33)]

# rename Quarter info
   Q1_17$Qt <-   "Q1_17"
   Q2_17$Qt <-   "Q2_17"
   Q3_17$Qt <-   "Q3_17"
   Q4_17$Qt <-   "Q4_17"
   Q1_18$Qt <-   "Q1_18"
   Q2_18$Qt <-   "Q2_18"
   Q3_18$Qt <-   "Q3_18"
   Q4_18$Qt <-   "Q4_18"
   
   #Name COlumn
   names(Q2_17) <- names(Q1_17)
   names(Q3_17) <- names(Q1_17)
   names(Q4_17) <- names(Q1_17)
   names(Q1_18) <- names(Q1_17)
   names(Q2_18) <- names(Q1_17)
   names(Q3_18) <- names(Q1_17)
   names(Q4_18) <- names(Q1_17)
   
   #Combine data 
      
   rm(mkt_Data)
   mkt_Data <- bind_rows(
   Q1_17,
   Q2_17,
   Q3_17,
   Q4_17,
   Q1_18,
   Q2_18,
   Q3_18,
   Q4_18)

  

    
head(mkt_Data)




# upate new Acocunt info 
custmap$KUNNR_OLD <- as.numeric(custmap$KUNNR_OLD)
custmap$KUNNR_NEW<- as.numeric(custmap$KUNNR_NEW)
mkt_Data <- mkt_Data[which(!is.na(mkt_Data$Customer)),]
unique(mkt_Data$Qt)
head(mkt_Data[which(is.na(mkt_Data$Customer)),])
mkt_Data <- left_join(mkt_Data, custmap, by = c("Customer" = "KUNNR_OLD"))
# View(mkt_Data[which(is.na(mkt_Data$KUNNR_NEW)),])

mkt_Data$KUNNR_NEW[which(is.na(mkt_Data$KUNNR_NEW))] <- mkt_Data$Customer[which(is.na(mkt_Data$KUNNR_NEW))]


#Dropping some Text values from full data 
mkt_Datalean <- mkt_Data[,-c(1,2,3,4,5,6,7,8,7)]

# mkt_s getting data in from of customer and Qt spending

mkt_cust_qt <- mkt_Datalean %>% group_by(KUNNR_NEW,Qt) %>% summarise(order_unit = sum(`Order Quantity`))
mkt_cust_qt <- spread(mkt_cust_qt,Qt,order_unit)


# Create Sample A of 1000 customer  

custA <- mkt_cust_qt[sample(nrow(mkt_cust_qt),1000),]
custAG <- gather(custA, key = "Qt",value = "order_unit",-KUNNR_NEW)
custAG$KUNNR_NEW <- as.character(custAG$KUNNR_NEW)
custAG$order_unit[which(is.na(custAG$order_unit))] <- 0

plot(custA)
ggplot(custAG,mapping = aes(x=KUNNR_NEW ,y= order_unit, color=Qt)) + geom_point()

ggplot(custAG,mapping = aes(y=KUNNR_NEW ,x= order_unit, color=Qt)) + geom_point() + facet_wrap(~Qt) 

mkt_Data$KUNNR_NEW[which(is.na(mkt_Data$KUNNR_NEW))] 

custAG %>%
  group_by(Qt) %>% summarise(order_unit = sum(order_unit)) %>% 
  ggplot(mapping = aes(x= Qt,y=order_unit,fill = Qt)) + geom_col() +  geom_label(aes(label=order_unit))+
theme_light()


order(t$Qt[c(1,3,5,7,2,4,6,8)])

# > Check https://www.youtube.com/watch?v=SvKv375sacA
# > Try getting chi square test using porpatl differen of 1000 custoemr prove is speding in one qt is more or less in other following qt. 

```


```{r}

#------------------------------------------SAMPLE ----------------------


#Create sample 

# mkt_s <- sample_n(mkt_Data, size = 5000, replace = FALSE)
 mkt_s <-    bind_rows(
   Q1_17[sample(nrow(Q1_17),200),],
   Q2_17[sample(nrow(Q2_17),200),],
   Q3_17[sample(nrow(Q3_17),200),],
   Q4_17[sample(nrow(Q4_17),200),],
   Q1_18[sample(nrow(Q1_18),200),],
   Q2_18[sample(nrow(Q2_18),200),],
   Q3_18[sample(nrow(Q3_18),200),],
   Q4_18[sample(nrow(Q4_18),200),])

 
#mkt_s <- mkt_Data %>% sample_frac(0.05)

head(mkt_s[which(is.na(mkt_s$Customer)),])
unique(mkt_s$Qt)
mkt_s <- mkt_s[which(!is.na(mkt_s$Customer)),]
unique(mkt_s$Qt)
# mkt_s2 <- dplyr:: left_join(mkt_s, custmap, by = c("Customer" = "KUNNR_OLD"))

unique(mkt_s$Qt)
head(mkt_s[which(is.na(mkt_s$KUNNR_NEW)),])
install.packages("xlsx")
library("xlsx")
write.xlsx(mkt_s,"ap.xlsx",sheetName = "Sheet1", 
  col.names = TRUE, row.names = TRUE, append = FALSE)
write.xlsx(mkt_s2,"ap2.xlsx",sheetName = "Sheet1", 
  col.names = TRUE, row.names = TRUE, append = FALSE)


ggplot(mkt_s, mapping = aes(x= as.character(mkt_s$`Promotion Order Doll`), y= mkt_s$`Order Quantity`, color= mkt_s$`External Description`))+
  geom_point()+theme(axis.text.x = element_text(angle = 70, hjust = 1)) + facet_wrap(~mkt_s$Qt)

 # (nms <- names(read_excel(path=paste0(filePath,"/","2017_Q3.xlsx"), sheet="DATA",n_max = 0)))

# rm(Q1_17)
# rm(Q2_17)
# rm(Q3_17)
# rm(Q4_17)
# rm(Q1_18)
# rm(Q2_18)
# rm(Q3_18)
# rm(Q4_18)


#Dropping some Text values from sample 
mkt_s <- mkt_s[,-c(1,2,4,5,6,7,8,7)]

# mkt_s getting data in from of customer and Qt speding

cust_qt <- mkt_s %>% group_by(Customer,Qt) %>% summarise(order_unit = sum(`Order Quantity`))

spread(cust_qt,Qt,order_unit)
```


### Part 1 - Introduction

This is ales data of from last 2 year , grouped by location and and quarter info. Main 

 What is your research question? Why do you care? Why should others care?
 
 Does customer who baught more at the Quarter end , how did they perfrom during the followin quarter.
 Does customers buy more during the Quarter End
 


### Part 2 - Data

  # Data: Write about the data from your proposal in text form. Address the following points:
  # 
  # Data collection: Describe how the data were collected.

This data is sample of sales by promotion for last two year. Data was shared by Marketting team to evaluate the sales performance.

Note : For Confidencilaty names and numbers have been changed in the data.

  # Cases: What are the cases? (Remember: case = units of observation or units of experiment)
in This sample we have 1657 rows. Each row identify the Order from the given customer.

  # Variables: What are the two variables you will be studying? State the type of each variable.
  
  Order Quantity is Response variable here . It's Quantitative variable.
  Quarter `Qt`, is Independent varible , it's qualitative variable as we can't add them.
  
  Other qualitative variables: Brands,Promotions, Zipcode etc. 

  
  
  # Type of study: What is the type of study, observational or an experiment? Explain how you've arrived at your conclusion using information on the sampling and/or experimental design.
  
  We do studies to gather information and draw conclusions. The type of conclusion we draw depends on the study method used: In an observational study, we measure or survey members of a sample without trying to affect them. In a controlled experiment, we assign people or things to groups and apply some treatment to one of the groups, while the other group does not receive the treatment.

This is observational study.

  # Scope of inference - generalizability: Identify the population of interest, and whether the findings from this analysis can be generalized to that population, or, if not, a subsection of that population. Explain why or why not. Also discuss any potential sources of bias that might prevent generalizability.
  
Since data set is too big and would take too much computing power and machine time. To save time on computing I am keeping my sample size to 200 * 8 (each quarter from 2 year). These findings may be generlaized for the same customer and identify the posibility of sales .
  # Scope of inference - causality: Can these data be used to establish causal links between the variables of interest? Explain why or why not.
  Since its a observational study we can't make Casue and Effect inference from here, but it being an observational study it will have some info about customers spending pttern over the years and Quarter.


### Part 3 - Exploratory data analysis

  Perform relevant descriptive statistics, including summary statistics and visualization of the data. Also address what the exploratory data analysis suggests about your research question.
  


### Part 4 - Inference

  If your data fails some conditions and you can't use a theoretical method, then you should use simulation. If you can use both methods, then you should use both methods. It is your responsibility to figure out the appropriate methodology.

We will examine sample of data after tidying of the data in the below formt :

|Customer | Q1 | Q2 |
|---------|----|----|
|1|21 | 12|
|2|21 | 12|
|3|21 | 12|
|4|21 | 12|
|.|. | .|
|.|. | .|
|n|n | n|
  
  # Check conditions
  # Theoretical inference (if possible) - hypothesis test and confidence interval
  # Simulation based inference - hypothesis test and confidence interval
  # Brief description of methodology that reflects your conceptual understanding

### Part 5 - Conclusion
Write a brief summary of your findings without repeating your statements from earlier. Also include a discussion of what you have learned about your research question and the data you collected. You may also want to include ideas for possible future research.
# 

### References


### Appendix (optional)

Remove this section if you don't have an appendix









