---
title: "607 Week6 p2"
author: "Rajwant Mishra"
date: "March 6, 2019"
output:
 html_document:
    df_print: paged
    toc_float: true
    highlight: tango
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load the tidyverse
library(tidyverse)
library(lubridate)
library(stringr)
library(spelling)
library(DT)
spell_check_files("607_Week6_P2.rmd", ignore = character(), lang = "en_US")
```
[RpubLink](http://rpubs.com/Rajwantmishra/week6_607_p2of3)

### Package used 

 
 1. library(tidyverse)
 2. library(lubridate)
 3. library(stringr)
 4. library(spelling)
 5. library(DT)
 6. spell_check_files("607_Week6_P2.rmd", ignore = character(), lang = "en_US")
 


### About Data 
Data is from US disability, it list number of applications being submitted from online and offline . Objective is to find that if Online service has helped Gov. to get more application through online mode.
* Data has lots of problem 
 + Data is wide by Month, AND also Fiscal Year may Not equal to same year.
 
 
## Data Process   {.tabset .tabset-fade .tabset-pills}

* Data has lots of problem 
 + Data is wide by Month, AND also Fiscal Year may Not equal to same year, 
 
 
### Read Data 


 
 
```{r}


# Read in data
ssa <- read_csv("https://raw.githubusercontent.com/Rajwantmishra/msds/master/week5/ssadisability.csv")

# Take a look at how this was imported
glimpse(ssa)
# tbl_df(ssa)
datatable(ssa)


```

### Data Wrangling  {.tabset .tabset-fade .tabset-pills}
* Make Data long 
* Split the COlumn data into  multiple column
* Convert Months to 3 Char letter months abbreviations 
* Convert Fiscal Year to valid year
* Building Date by Months and Year and Date
* Converting it into right date fromat 

#### Working with Date

   
```{r}
# Make the dataset long by skipping Fiscal Year column
ssa_long <- gather(ssa, month, applications, -Fiscal_Year)

# Long  data 
datatable(ssa_long)



# Split the Month into  month and application type by "_" to split months and Type of application .(internet and Total )
ssa_long <- separate(ssa_long, month, c("month", "application_method"), sep="_")

# Data after split 
print(ssa_long, n=20)

# Checking Unique Months value , and we note that not all the Months have 3 char length 
unique(ssa_long$month)

# Convert month to standard abbreviations , as not all the months are in 3 Char string length. 
ssa_long$month <- str_sub(ssa_long$month,1,3)

# Check value for months 
unique(ssa_long$month)

# Check Value for Fiscal Year
unique(ssa_long$Fiscal_Year)

# Convert Fiscal_Year from alphanumeric strings to actual years
# Replce FY with 20
ssa_long$Fiscal_Year <- str_replace(ssa_long$Fiscal_Year, "FY", "20")

# What values do we now have for months?
unique(ssa_long$Fiscal_Year)

# Build a date string using the first day of the month
paste('01', ssa_long$month, ssa_long$Fiscal_Year)
# Convert date to right date format. 
ssa_long$Date <- dmy(paste("01", ssa_long$month, ssa$Fiscal_Year))

# Check final date after applying DMY 
unique(ssa_long$Date)
```


#### Working with Fiscal Yr
  >  
   Government fiscal years differ from calendar years in that they are named for the
   calendar year where they end.  The government fiscal year begins in October.
   So October 2016 is actually in FY17.
   We need to convert these to calendar dates before we try to plot them, so we 
   need to find months >=10 and subtract one year from them
   
```{r}
# Government fiscal years differ from calendar years in that they are named for the
# calendar year where they end.  The government fiscal year begins in October.
# So October 2016 is actually in FY17.
#
# We need to convert these to calendar dates before we try to plot them, so we 
# need to find months >=10 and subtract one year from them

# Let's find the affected rows
advanced_dates <- which(month(ssa_long$Date)>=10)

# And then decerement the years by one
year(ssa_long$Date[advanced_dates]) <- year(ssa_long$Date[advanced_dates]) - 1

datatable(ssa_long)

# Let's look at where we are
summary(ssa_long)
```

### Analysis

```{r}
# Remove Fiscal_Year and month columns
ssa_long$Fiscal_Year <- NULL
ssa_long$month <- NULL

# Convert application_method to a factor
ssa_long$application_method <- as.factor(ssa_long$application_method)

# Checking the data summary now.
summary(ssa_long)

# Widen the final dataset, moving Appliation Method side by side in a row  for the moth.
ssa <- spread(ssa_long, application_method, applications)

# Data view after spread
datatable(ssa)

# Add a column for the percentage of applications that were online
ssa$online_percentage <- ssa$Internet/ssa$Total*100
ssa$Offline_percentage <- 100 - ssa$online_percentage
ssa <- ssa[which(!is.na(ssa$Total)),]

# Plot the results
ggplot(data=ssa, mapping=aes(x=Date,y=online_percentage)) +
  geom_point()+
  geom_line()+
labs(title = "Type of Applicaiton Flow by Year")

plot_vline <- filter(ssa,ssa$online_percentage> ssa$Offline_percentage)$Date[1]
ggplot(data=ssa, mapping=aes(x=Date)) +
  geom_line(aes(y=Offline_percentage, colour="darkblue"),size=1 )+
  geom_line(aes(y=online_percentage, colour="darkred"),size=1 )+
scale_color_discrete(name = "Type ", labels = c("Offline_percentage","online_percentage"))+
    labs(title = "Type of Applicaiton Flow by Year")+
  geom_vline(xintercept = plot_vline,color="blue")+
  geom_text( mapping=aes(x=plot_vline+1, y=55, label=" Internet  > Offline "), size=4, angle=90, vjust=-0.4, hjust=0) 

 


  

```

### Conclusion

Based on the above data points and progress of the Internet application over year , we can say that Internet applications are growing over the year and its helping Gov to reduce the traffic of the offline request. 
