---
title: "607 Week6 P3"
author: "Rajwant Mishra"
date: "March 6, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load the tidyverse and the dataset
library(tidyverse)
library(DT)
```


## About Dataset 
  # Attribute Information: 
  # > 1. age 
  # > 2. sex 
  # > 3. chest pain type (4 values) 
  # > 4. resting blood pressure 
  # > 5. serum cholestoral in mg/dl 
  # > 6. fasting blood sugar > 120 mg/dl ( )
  # > 7. resting electrocardiographic results (values 0,1,2)
  # > 8. maximum heart rate achieved 
  # > 9. exercise induced angina 
  # > 10. oldpeak = ST depression induced by exercise relative to rest 
  # > 11. the slope of the peak exercise ST segment 
  # > 12. number of major vessels (0-3) colored by flourosopy 
  # > 13. thal: 3 = normal; 6 = fixed defect; 7 = reversable defec
  # > 14. target 1= Probelm or 0 (NO Probelm )
  
```{r}

# ageage in years
# sex(1 = male; 0 = female)
# cpchest pain type
# trestbpsresting blood pressure (in mm Hg on admission to the hospital)
# cholserum cholestoral in mg/dl
# fbs(fasting blood sugar > 120 mg/dl) (1 = true; 0 = false)
# restecg resting electrocardiographic results
# thalach maximum heart rate achieved
# exangexercise induced angina (1 = yes; 0 = no)
# oldpeakST depression induced by exercise relative to rest
# slopethe slope of the peak exercise ST segment
# canumber of major vessels (0-3) colored by flourosopy
# thal3 = normal; 6 = fixed defect; 7 = reversable defect
# target 1= Probelm or 0 (NO Probelm )



# ctype = c("numeric","factor","numeric","numeric","numeric", "boolean","numeric","numeric","boolean","double","numeric","numeric","numeric","boolean")
# 
# ctype1 = c(col_integer(),col_logical(),col_integer(),col_integer(),col_integer(), col_logical(),col_integer(),col_integer(),col_logical(),col_double(),col_double(),col_double(),col_double(),col_logical())
# 
# # "text","text","text","text","text","text","text")


hdata <- read_csv('https://raw.githubusercontent.com/Rajwantmishra/msds/master/607/Week6/data1/heart.csv',col_types = cols(
  age = col_double(),
  sex = col_factor(),
  cp = col_double(),
  trestbps = col_double(),
  chol = col_double(),
  fbs = col_logical(),
  restecg = col_double(),
  thalach = col_double(),
  exang = col_logical(),
  oldpeak = col_double(),
  slope = col_double(),
  ca = col_factor(),
  thal = col_factor(),
  target = col_logical())
)

datatable(hdata)
```

## Analysis 

Here I haev decided to find Entropy of Traget varible for each observation present in the dataset. 


```{r eval=FALSE, include=FALSE}
# install.packages("entropy")
library(entropy)
library(tidyverse)
table(hdata$target)

group_by(hdata,hdata$target)%>%summarise(probTarget = median(trestbps))

entropy(hdata$age)
prop.table(table(hdata$age))
hdata$age <- as.numeric(hdata$age)


IG_cat(hdata,'age',c("target"))
weights <- information.gain(age~., hdata,unit = "log2")
  print(weights)

entropy(0.7)

Eage <- data.frame(prop.table(table(hdata$age)))

```

```{r eval=FALSE, include=FALSE}
# load entropy library
library("entropy")
### 1D example ####
# sample from continuous uniform distribution
x1 = runif(10000)
hist(x1, xlim=c(0,1), freq=FALSE)
# discretize into 10 categories
y1 = discretize(x1, numBins=10, r=c(0,1))
y1
# compute entropy from counts
entropy(y1) # empirical estimate near theoretical maximum



# observed counts for each bin
y = c(1,1,1,2,2,2,2,2,2,2)
prop.table(table(y))
sum((prop.table(table(y))*log2(prop.table(table(y))))*-1)



y = c(0,4,3,6,7,3,2,3,4,5)
prop.table(table(y))
sum((prop.table(table(y))*log2(prop.table(table(y))))*-1)
entropy(y)

p <- table(y); 
p <- p/sum(p); 
sum(-p*log(p))




entropy(c(16,14))
entropy(y, method="ML")
entropy(y, method="MM")
entropy(y, method="Jeffreys")
entropy(y, method="Laplace")
entropy(y, method="SG")
entropy(y, method="minimax")
entropy(y, method="CS")
#entropy(y, method="NSB")
entropy(y, method="shrink")
entropy.empirical(y)

```
```{r}
pt <- 30
ps <- 14
pd <- 16

pg50<- 13
pl50 <- 17

pg50s <- (12/16) * (1/14)
pg50s

```

```{r eval=FALSE, include=FALSE}
 data(iris)

# install.packages("FSelector")
library( FSelector)
data(iris)

  weights <- information.gain(Species~., iris)
  print(weights)
  subset <- cutoff.k(weights, 2)
  f <- as.simple.formula(subset, "Species")
  print(f)

  weights <- information.gain(Species~., iris, unit = "log2")
  print(weights)

  weights <- gain.ratio(Species~., iris)
  print(weights)
  subset <- cutoff.k(weights, 2)
  f <- as.simple.formula(subset, "Species")
  print(f)

  weights <- symmetrical.uncertainty(Species~., iris)
  print(weights)
  subset <- cutoff.biggest.diff(weights)
  f <- as.simple.formula(subset, "Species")
  print(f)


```
```{r eval=FALSE, include=FALSE}
y = c(1,1,1,2,2,2,2,2)
prop.table(table(y))
sum((prop.table(table(y))*log2(prop.table(table(y))))*-1)
entropy(y)



y = c(1,1,1,2,2,2,2,2)
prop.table(table(y))
sum((prop.table(table(y)) * log2(prop.table(table(y))))*-1)
entropy(y)
sum((3/8 *log2(3/8))     +     (5/8 *log2(5/8)))

sum((9/16 *log2(9/16))     +     (7/16 *log2(7/16)))

sum((8/16 *log2(8/16))     +     (8/16 *log2(8/16)))

entropy(y)

data(iris)
unique(iris$Species)
prop.table(table(iris$Species))
weights <- information.gain(Species~., iris)

 weights <- information.gain(Species~., iris, unit = "log2")
  print(weights)
 subset <- cutoff.k(weights, 2)

f <- as.simple.formula(subset, "Species")
print(f)



weights <- information.gain(age~., hdata,unit = "log2")
 weights <- information.gain(Species~., iris, unit = "log2")
entropy(iris$Species)
IG_numeric(iris, "Sepal.Length","Species")
IG_numeric(iris, "Sepal.Width","Species")
IG_numeric(iris, "Petal.Length","Species")
IG_numeric(iris, "Petal.Width","Species")
  print(weights)

  IG_cat(iris, "Sepal.Length","Species")
IG_cat(iris, "Sepal.Width","Species")
IG_numeric(iris, "Petal.Length","Species")
IG_numeric(iris, "Petal.Width","Species")
IG_cat(data,feature,target)

```


```{r}
# https://stackoverflow.com/questions/3289589/can-the-value-of-information-gain-be-negative?answertab=active#tab-top

library(plyr)
#compute Shannon entropy
entropy <- function(target) {
  freq <- table(target)/length(target)
  # vectorize
  vec <- as.data.frame(freq)[,2]
  #drop 0 to avoid NaN resulting from log2
  vec<-vec[vec>0]
  #compute entropy
  -sum(vec * log2(vec))
}

#returns IG for numerical variables.
IG_numeric<-function(data, feature, target, bins=4) {
  #Strip out rows where feature is NA
  data<-data[!is.na(data[,feature]),]
  #compute entropy for the parent
  e0<-entropy(data[,target])
  
  data$cat<-cut(data[,feature], breaks=bins, labels=c(1:bins))
  
  dd_data<-ddply(data, "cat", here(summarise), 
                 e=entropy(get(target)), 
                 N=length(get(target)),
                 min=min(get(feature)),
                 max=max(get(feature))
                 )
  
  #calculate p for each value of feature
  dd_data$p<-dd_data$N/nrow(data)
  #compute IG
  IG<-e0-sum(dd_data$p*dd_data$e)
  
  return(IG)
}

#returns IG for categorical variables.
IG_cat<-function(data,feature,target){
  #Strip out rows where feature is NA
  data<-data[!is.na(data[,feature]),] 
  #use ddply to compute e and p for each value of the feature
  dd_data<-ddply(data, feature, here(summarise), e=entropy(get(target)), N=length(get(target)))
  #compute entropy for the parent
  e0<-entropy(data[,target])
  #calculate p for each value of feature
  dd_data$p<-dd_data$N/nrow(data)
  #compute IG
  IG<-e0-sum(dd_data$p*dd_data$e)
  
  return(IG)
}


# data <- iris
# feature <- "Petal.Length"
# bins  <- 50 
# data$cat<-cut(data[,feature], breaks=bins, labels=c(1:bins))
#  
#   dd_data<-ddply(data, "cat", here(summarise), 
#                  e=entropy(get(target)), 
#                  N=length(get(target)),
#                  min=min(get(feature)),
#                  max=max(get(feature))
#                  )
#    dd_data$p<-dd_data$N/nrow(data)
# 
# ggplot(dd_data,aes(x=N,y= e,fill=cat))+geom_col()

 
 EntropyGraph <- function(data,target,var = NA) {

  
   
   if (is.na(var)){
     
       #use ddply to compute e and p for each value of the feature
  for (i in 1:length(data)){
     if(names(data[i])==target){next}
      #Strip out rows where feature is NA
     data<-data[!is.na(data[,names(data[i])]),] 
     dd_data<-ddply(data, names(data[i]), here(summarise), e=entropy(target), N=length(target))
     dd_data$p <- as.data.frame(prop.table(table(data[i])))[[2]]
      # assign(paste0("EPLT",names(data[i])),
      #        ddply(data, names(data[i]), here(summarise), e=entropy(target), N=length(target)))
      # print (names(data[i]))
  
    g <- ggplot(dd_data,aes(x=p,y= e,fill=get(names(data[i]))))
          g <- g+ geom_col(position = "dodge") 
          g <- g+ ggtitle(paste("Entropy proportion of",names(data[i]), "for Target: ",target)) 
          g <- g +geom_text(aes(label = get(names(data[i]))),color="red")
          # g <- g +geom_text(aes(label = p),color="green",nudge_x = .5)
          g <- g+ ylab("Entropy") + xlab("Proportion") 
          g <- g+  guides(fill=guide_legend(title=names(data[i])))
        # g <- g+ geom_rect(mapping=aes(xmin= median(p) ,xmax= max(p),ymin=0,ymax=max(e),color="green"),color="black", alpha=0.01)
           g <- g +    geom_rect(mapping=aes(xmin= .5,xmax=1,ymin=0,ymax=.5,color="green"),color="red", alpha=0)

        print(g)
    }
     
   }else{
           #use ddply to compute e and p for each value of the feature
      for (i in 1:length(data)){
        if(names(data[i])!=var){next}
          #Strip out rows where feature is NA
      data<-data[!is.na(data[,names(data[i])]),] 
         dd_data<-ddply(data, names(data[i]), here(summarise), e=entropy(target), N=length(target))
         dd_data$p <- round(as.data.frame(prop.table(table(data[i])))[[2]],2)
          # assign(paste0("EPLT",names(data[i])),
          #        ddply(data, names(data[i]), here(summarise), e=entropy(target), N=length(target)))
          # print (names(data[i]))
      
         g <- ggplot(dd_data,aes(x=p,y= e,fill=get(names(data[i]))))
          g <- g+ geom_col(position = "dodge") 
          g <- g+ ggtitle(paste("Entropy proportion of",names(data[i]), "for Target: ",target)) 
          g <- g +geom_text(aes(label = get(names(data[i]))),color="red",nudge_y = 0.01)
           g <- g +geom_text(aes(label = p),color="green",nudge_x = .5)
          g <- g+ ylab("Entropy") + xlab("Proportion") 
          g <- g+ guides(fill=guide_legend(title=var))
          #g <- g+ geom_rect(mapping=aes(xmin= median(p) ,xmax= max(p),ymin=0,ymax=max(e),color="green"),color="black", alpha=0.01)
          g <- g +    geom_rect(mapping=aes(xmin= .5,xmax=1,ymin=0,ymax=.5,color="green"),color="red", alpha=0)
          g <- g + geom_point(aes(shape=names(data[i]),color=names(data[i])))

            
        print(g)
      }
     
   }
  
 }

 
  
  EntropyGraph(hdata,"target")
  EntropyGraph(hdata,"target","age")
  EntropyGraph(hdata,"target","cp")
  # slope
  # oldpeak
  # thal
  
```



```{r}
# 
# Attribute Information: 
# > 1. age 
# > 2. sex 
# > 3. chest pain type (4 values) 
# > 4. resting blood pressure 
# > 5. serum cholestoral in mg/dl 
# > 6. fasting blood sugar > 120 mg/dl ( )
# > 7. resting electrocardiographic results (values 0,1,2)
# > 8. maximum heart rate achieved 
# > 9. exercise induced angina 
# > 10. oldpeak = STf the peak exercise ST segment 
# > 12. number of depression induced by exercise relative to rest 
# > 11. the slope o major vessels (0-3) colored by flourosopy 
# > 13. thal: 3 = normal; 6 = fixed defect; 7 = reversable defec
# target 1= Probelm or 0 (NO Probelm )


  
  
  # Lets take only TARGET = FALSE 
  hdataT <- filter(hdata,target==TRUE) 
    EntropyGraph(hdataT,"target")
    
    #     Bases on above data points we can say that imporant varaible to check Heart probelm can be : 
    #       slope = 2
    # ca= 0
    # thal = 2
    # exang= false
    # fbs = false
    # restecg = 1
    
  hdataF <- filter(hdata,target==FALSE) 
    EntropyGraph(hdataF,"target") 
    
    # Based on this data we can say that with following points we can have healhy heart. 
    # FASLE
# sex = 1
# cp = 0
# fbs = false
# slop = 1
# thal = 3
    
    EntropyGraph(hdataF,"target","fbs") 
    EntropyGraph(hdataT,"target","fbs") 
    # SInce FBS it can be noted that FBS is not very imporant as it tends to show negative result with other varaibles . FBS is FALSE ~ 86%  in population with heart probelm . whereas its 84% in case where heart probelm is not present . Even though entropy of this varible is not not leading us to a pure dataset mix, but avaibility of its in conjustion with varaible can be used to build the model. 
    
    # Lets break it further. checking thal 
    
 EntropyGraph(hdataF,"target","thal") 
    EntropyGraph(hdataT,"target","thal") 
    
    # Thal = 2 is 79% strong variable which can be a good indicator of good heart health. 
    # similarly Thal = 3 is also bad indicator of heart heath with 64% porobability . 
    
    
# Lets see if entropy with Target is really ZERO when Thal ==3
DT::datatable(filter(hdataF,thal==3))    
    
    
    # ----------------------------------------------------
  
    r <- ddply(hdataT, "oldpeak", here(summarise), e=entropy(get("target")), N=length(get("target")))
  r$p<- as.data.frame(prop.table(table(hdataT$fbs)))[[2]]
 ggplot(r,aes(x=p,y= e,fill=oldpeak))+geom_col(position="dodge")+
    geom_text(aes(label = oldpeak),color="red")+
   geom_rect(mapping=aes(xmin= .5,xmax=1,ymin=0,ymax=.5,color="green"),color="red", alpha=0)
 
 # ggplot(r,aes(x=p,y= e,fill=fbs))+geom_point(aes(shape=fbs,color=fbs))+geom_col(position="dodge")
 
 
  table(filter(hdata,fbs==TRUE)$target)

```



```{r}
  hdata  

gather(hdata,key = "R1", value = "RAJ",)


```

```{r eval=FALSE, include=FALSE}



  weights <- information.gain(Species~., iris, unit = "log2")
# 
# 
 r <- ddply(hdata, "age", here(summarise), e=entropy(get("target")), N=length(get("target")))

 ggplot(r,aes(e,fill =  N))+
   geom_bar(position = "dodge")
 table(hdata$age)
#  
#   r <- ddply(hdata, "chol", here(summarise), e=entropy(get("target")), N=length(get("target"))) 
#  
 
 table(r$age)
 
  r <- ddply(hdata, "age", here(summarise), e=entropy(get("target")), N=length(get("target")))
 
  r$p<- prop.table(table(hdata$age))
 
  ggplot(r,aes(x=p,y= e,fill=age))+geom_col( position="dodge")+
  geom_text(aes(label = age),color="red")
   
 
  filter(hdata,age %in% c(54,59,57))
 
 
  r <- ddply(hdata, "cp", here(summarise), e=entropy(get("target")), N=length(get("target")))
  r$p<- as.data.frame(prop.table(table(hdata$cp)))[[2]]
 ggplot(r,aes(x=p,y= e,fill=cp))+geom_col(position="dodge")+
    geom_text(aes(label = cp),color="red")+
   geom_rect(mapping=aes(xmin= .5,xmax=1,ymin=0,ymax=.5,color="green"),color="black", alpha=0.09)
 
   ggplot(r,aes(x=p,y= e))+geom_bar(stat="identity")+
  geom_text(aes(label = cp),position ="stack",color="red")
      
  
  
 ggplot(r,aes(e,fill =  N))+
   geom_bar(position = "dodge")
    geom_text(aes(label = age),position =     "stack",color="red")
  
    
    
  ggplot(data = r) + 
  geom_bar(mapping = aes(x = e, fill = N), position = "dodge2")
  
#  
#  ggplot(ssaDF, aes(y = delayed, x = FlyingFrom,fill= AirPort)) + 
#   geom_bar(stat = "identity",position="dodge")
#  
#  
#  table(hdata$age)



```






